TBD

### 2016-09-26 paper.tex
Started to load antenna layout figures

\title[Dust envelopes around RV Tauri stars]{Dust envelopes around RV Tauri stars}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$Indian Institute of Astrophysics, Bangalore 560034, India\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}
In the {\it IRAS\/} [12]--[25],  [25]--[60] colour--colour diagram, RV
Tauri stars are found to populate cooler temperature regions
$(T<600\,\rmn{K})$, distinctly different from those occupied by  the
oxygen and carbon Miras. The {\it IRAS\/} fluxes are  consistent with the
dust density in the envelope varying as the inverse square of the
radial distance, implying that the grain formation processes in these
objects are most probably continuous and not sporadic. It is found that
the spectroscopic subgroups A and B are well separated in the
far-infrared two-colour diagram, with group B objects having
systematically cooler dust envelopes. We interpret this as being due to
a difference in the nature of grains, including the chemical
composition, in the two cases.
\end{abstract}

@@

\begin{figure*}
\centering
\subfigure[full-complex:   Real]
{\includegraphics[width=0.33\textwidth]{./HEX_lay.pdf}\label{fig:stef_r}}
\subfigure[full-complex:  Imag]
{\includegraphics[width=0.33\textwidth]{./SQR_lay.pdf}\label{fig:stef_i}}
\subfigure[full-complex: ghost pattern]
{\includegraphics[width=0.33\textwidth]{./REG_lay.pdf}\label{fig:full_pat_45}}

\subfigure[phase-only:   Real]
{\includegraphics[width=0.33\textwidth]{./HEX_phi.pdf}\label{fig:phase_r}}
\subfigure[phase-only:   Imag]
{\includegraphics[width=0.33\textwidth]{./SQR_phi.pdf}\label{fig:phase_i}}
\subfigure[phase-only: ghost pattern]
{\includegraphics[width=0.33\textwidth]{./REG_phi.pdf}\label{fig:phase_pat_45}}
\caption{scenario. \label{fig:ghost_pattern_bas_45}}
\end{figure*}

>>>>

\title[Unknown]{TBD}
\author[A. V. Raveendran and A. N. Other]{A. V. Raveendran$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$Indian Institute of Astrophysics, Bangalore 560034, India\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{abstract}
TBD
\end{abstract}

@@

\begin{figure*}
\centering
\subfigure[Hexagonal layout]
{\includegraphics[width=0.33\textwidth]{./HEX_lay.pdf}\label{fig:HEX_lay}}
\subfigure[Square layout]
{\includegraphics[width=0.33\textwidth]{./SQR_lay.pdf}\label{fig:SQR_lay}}
\subfigure[Regular east-west layout]
{\includegraphics[width=0.33\textwidth]{./REG_lay.pdf}\label{fig:REG_lay}}

\subfigure[Hexagonal: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./HEX_phi.pdf}\label{fig:HEX_phi}}
\subfigure[Square: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./SQR_phi.pdf}\label{fig:SQR_phi}}
\subfigure[Regular east-west: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./REG_phi.pdf}\label{fig:REG_phi}}
\caption{In the top panel we have three different redundant antenna layouts. In the bottom panel we have the symmetric redundancy geometry mapping $\zeta_{ij}$
of each of the layouts in the top panel.}
\end{figure*}
